### 2016-07-26 notions.tex
comments on relationships between correctness and privacy notions
cheers

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries.  } \tsnote{Do you mean to
  assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
  because these are pointless?  Otherwise, I don't see a need for restrictions.}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

@@

\medskip
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\
}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion. (Still playing...)} 
\label{fig:privacy}
\end{figure}

>>>>

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
  This says that security is required \emph{only} for properties that are
  true of both sets.  So a scheme with $M=S$ will be trivially secure
  against set membership queries.  } \tsnote{Do you mean to
  assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
  because these are pointless?  Otherwise, I don't see a need for restrictions.} \tsnote{Maybe we restrict from queries~$q$ that would have the same value for all sets~$S \in \calS$?  (Or all sets of the same size, or...?)}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

@@

\medskip
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\aux,q)$\\
Return~$a$\\
}
}
\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
  definitions. The top is a weaker notion, because the representation
  is hidden from the adversary. {\bf Right:} An
  ``indistinguishability'' style notion. (Still playing...) \textcolor{red}{on the right, should $S_0,S_1$ be sampled from $\distr{\calS}{}$ instead?  This would be in line with the other notions}} 
\label{fig:privacy}
\end{figure}
